The influence of massive early merger events on the chemo-dynamics of galaxy discs

### 2022-10-25 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}
    \script{half_mass_radius_gas.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/279e12_gas_size.pdf}
        \caption{
            Half mass radius of the cold gas as a function of time. The sharp increases in the cold gas size around 2 Gyr and 9 Gyr indicate the influence of massive gas rich merger events on the galaxy. The addition of fresh cold gas leads to a sudden increase in cold gas half mass size.
        }
        \label{fig:half_mass}
    \end{centering}
\end{figure}

@@

\begin{figure}
    \script{gas_profile.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/2.79e12_gas_profile_2d.pdf}
        \caption{
            Surface density profile of the cold gas before and after the two merger events. Outside of a radius of 5 kpc the merging satellites contribute cold gas up to a factor of 4 in surface density.
        }
        \label{fig:surf_den}
    \end{centering}
\end{figure}

>>>>

%\begin{figure}
%    \script{half_mass_radius_gas.py}
%    \begin{centering}
%        \includegraphics[width=\linewidth]{figures/279e12_gas_size.pdf}
%        \caption{
%            Half mass radius of the cold gas as a function of time. The sharp increases in the cold gas size around 2 Gyr and 9 Gyr indicate the influence of massive gas rich merger events on the galaxy. The addition of fresh cold gas leads to a sudden increase in cold gas half mass size.
%        }
%        \label{fig:half_mass}
%    \end{centering}
%\end{figure}

@@

\begin{figure}
    \script{gas_profile_all.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/gas_profile_2d.pdf}
        \caption{
            Relative change in cold gas surface density profile before and after the merger events. Outside of a radius of $\sim5$ kpc the merging satellites contribute cold gas up to a factor of 4 in surface density.
        }
        \label{fig:surf_den}
    \end{centering}
\end{figure}
